Safe Memory Regions for Big Data Processing

### 2016-06-15 paper/type-inference.tex
type inference

\paragraph{Constraint Generation.}

@@

\subsection{Elaboration and Constraint Generation}

>>>>

\paragraph{Constraint Generation.}
The constraint generation algorithm is a direct adaption of the type checker:
each type checking rule is modified to produce a set of constraints that must hold
for the type checker to succeed.
%
Fig.~\ref{fig:constraint-gen} illustrates this for the object allocator \C{new} construct.

@@

\subsection{Elaboration and Constraint Generation: Details}
